{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-05-23 thesis/quicksand.tex
work on quotes
update quicksand chapter quote

\chapter{Quicksand}
\label{chap:quicksand}
\inspirationalquote{
% original
% {\footnotesize 嫌な事も悲しい事もあったけど、守りたい物だって沢山この世界にはあったから…} \\
% trans. slightly paraphrased from crunchyroll subtitle; removed "..."s, added past tense for あった
There were awful, sad things in this world.
But there were a lot of things worth protecting, too.
}
{Kaname Madoka, Mahou Shoujo Madoka{\raisebox{0.1em}{$\scriptstyle \bigstar$}}Magica}
%\inspirationalquote{Always, somewhere, someone is fighting for you.
%As long as you remember her, you are not alone.}
%{Mahou Shoujo Madoka{\raisebox{0.1em}{$\scriptstyle \bigstar$}}Magica}

>>>>

\chapter{Quicksand}
\label{chap:quicksand}
\inspirationalquote{
% original - TODO, put in
%{\footnotesize 嫌な事も悲しい事もあったけど、守りたい物だってたくさんこの世界にはあったから。} \\
There are awful, sad things in this world.
But there are a lot of things worth protecting, too.
}
%{Kaname Madoka, Mahou Shoujo Madoka{\raisebox{0.1em}{$\scriptstyle \bigstar$}}Magica}
{Kaname Madoka, Puella Magi Madoka{\raisebox{0.1em}{$\scriptstyle \bigstar$}}Magica}
%\inspirationalquote{Always, somewhere, someone is fighting for you.
%As long as you remember her, you are not alone.}
%{Mahou Shoujo Madoka{\raisebox{0.1em}{$\scriptstyle \bigstar$}}Magica}
